%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------




\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Divyanshu Verma} \\ \vspace{1pt}
    Bihar, India  \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 9631467452 ~ \href{mailto:divyanshuvermaji@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{divyanshuvermaji@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/divyanshuan/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/divyanshuan}}  ~
    \href{https://github.com/divyanshuan}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/divyanshuan}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Central University of Haryana, Haryana}{Sep 2020 -- June 2024}
      {Bachelor of Technology (CSE)}{8.58 CGPA}
    \resumeSubheading
      {L.M. Collage, Gaya}{July 2017 -- May 2019}
      {B.S.E.B (Class XII)}{84\% }
  \resumeSubHeadingListEnd


%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item\small Data Structures
                \item Software Engineering
                \item Algorithms Analysis
                \item Database Management
                \item Computer Network
                \item Operating System
                \item Computer Architecture
                \item Machine Learning
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd
    
%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C++, JavaScript, HTML, CSS, SQL} \\
     \textbf{Technologies/Frameworks}{: React.Js, Django (Django Rest API’s), Next.js, Axios, Node.js, Express.Js, Tailwind CSS} \\
     \textbf{Database}{: MySQL, MongoDB} \\
     \textbf{Developer Tools}{: Linux, Git, GitHub, Docker, Postman, VS Code, Figma} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {StarOps Technologies Pvt. Ltd.}{Oct 2023 -- Present}
      {Software Development Intern}{Greater Noida}
      \resumeItemListStart
        \resumeItem{Led frontend development for the \textbf{Udharibazaar} using \textbf{React, Tailwind CSS,  Material-UI}.}
        \resumeItem{Developed reusable components in React.js that can be utilized across multiple projects, improving development efficiency by 20\%.}
        \resumeItem{Implemented performance optimization techniques, including code splitting and lazy loading in React.js projects, reducing page load times by 40\% and improving website performance.}
        \resumeItem{Mastered \textbf{Postman} for API testing, fortifying application robustness and performance.}
        \resumeItem{Crafted responsive and intuitive user interfaces to deliver a seamless and visually appealing user experience, resulting in a
20\% increase in user satisfaction scores based on post-deployment feedback surveys.
}
      \resumeItemListEnd

    \resumeSubheading
      {Siraom Pvt. Ltd.}{April 2023 -- August 2023}
      {FullStack Developer Intern}{Pune, Maharashtra}
      \resumeItemListStart
        \resumeItem{Deployed cache optimization techniques using the Laravel framework to significantly enhance website performance. This initiative resulted in a notable improvement in the browsing experience, increasing smoothness from 60\% to 96\%.}
        \resumeItem{Developed \textbf{Image compression} feature from the ground up, leveraging the capabilities of the \textbf{Intervention Image} library. This resulted in 40\% enhancement in the website's loading performance.}
        \resumeItem{Orchestrated impactful UI improvements using the Laravel framework, enhancing aesthetics and design strategy. This led to increased user engagement and a visually enriched website experience.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{UdhariBazaar} $|$ \emph{React, Tailwind CSS, Django, SQL}}{Oct 2023 -- Present}
          \resumeItemListStart
            \resumeItem{Created a comprehensive web application to facilitate loan applications for home, business, and car loans.}
            \resumeItem{Integrated APIs from various loan providers to automate the application process, reducing processing time by 50\%.}
            \resumeItem{Improved overall performance through strategic utilization of libraries and optimization techniques, resulting in a 30\% increase in application throughput and enhanced user satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{Centralised Tuition Management System} $|$ \emph{React.Js, Laravel, Bootstrap, SQL}}{October 2022}
          \resumeItemListStart
            \resumeItem{Centralized student data storage across branches, eliminating duplication and ensuring accurate records management.}
            \resumeItem{Empowered branch managers with direct access to branch-specific data, facilitating autonomous updates of student information and administrative tasks.}
            \resumeItem{Implemented a smooth fee management system, enabling branch managers to input, track due dates, and monitor payments, ensuring effective financial control.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}





%-----------INVOLVEMENT---------------
\section{Extracurricular}
    % \resumeSubHeadingListStart
        % \resumeSubheading{Fraternity}{Spring 2020 -- Present}{President}{University Name}
            \resumeItemListStart
            \vspace{-1pt}
                \resumeItem{Coordinated 10+ events with 60+ registrations each as \textbf{Co-Team Manager} for ByteCodeLearners Community, fostering collaborative learning and skill development.}
                \vspace{-3pt}
                \resumeItem{Managed data compilation for 20+ events and over 1100 registrations as Core Team member of \textbf{Advik23}. }
                
            \resumeItemListEnd
        
    % \resumeSubHeadingListEnd

\end{document}
